Adopting agile in the large: motivations, success factors and challenges

### 2014-05-18 journal/article.tex
Improved inclusion facets

Based on the research questions and intended focus of the research, we defined
three facets to guide inclusion/exclusion decisions: agile software engineering,
focus on transformation, and large scale. The first facet covers primary studies
focusing on software engineering organizations applying or striving to apply
agile methods. The second facet states that included studies must provide
insights relevant to organizational transformation, and specifically to the
research questions. The third facet underlines the particular contribution we
aim to provide with this research, namely the exclusive focus on large
organizations. These three facets were used for inclusion and exclusion in each
study selection step, including search string design, filtering by abstracts,
and full text filtering.

@@

Transformation and ``scaling up'' are very closely related and in some cases
they are one and the same. For instance, if transformation begins with a pilot
and spreads gradually through the organization, the process can very well be
seen as a ``scaling up'' journey. However, we excluded cases where a initially
small organization was scaled up \cite{Maranzato2012}, and discussions with a
process centered viewpoint without describing organizational change
\cite{Lyon2008}.
% Also [Greening 2010] on process centered viewpoint without transformation

@@

In addition to the criteria listed above we excluded studies that were not
empirical. We excluded textbooks, studies merely presenting theories, and other
studies that did not include any case organization. We also excluded studies of
benefits or limitations of agile in general. Lastly, we excluded student
experiments as it is implausible to simulate the dynamics of a large
organization in an experiment.

@@

We constructed a search string based on the facets \emph{agile software
deveolpment} and \emph{organizational transformation}, as presented in section
\ref{sec:inclusioncriteria}. Preliminary searches had showed that picking
keywords with good precision was difficult. Therefore we decided to exclude the
facet \emph{large scale} from the keyword search, with the consequence of
increasing the manual filtering effort in the subsequent steps.
Having a substantial part of the matches in non-relevant areas such as agile
manufacturing, we included only articles including the term ``software'' or
articles published in relevant conferences. Instead of engineering the search
terms any further, which proved to result in excluding some relevant articles,
we chose to rely more on manual filtering. The resulting facets and keywords are
listed in Table \ref{table:searchterms}.

@@

Full text filtering was performed by evaluating each article against the three
facets of the inclusion criteria. Filtering was done in two steps. In the first
step Dikert extracted data relevant to the three facets of the inclusion
criteria. Based on the extracted data 76 papers could be immediately deemed as
included or excluded. The remaining 94 papers were evaluated against the
inclusion criteria by both Dikert and Paasivaara, and a decision was made after
discussing each paper separately. In difficult cases Lassenius was consulted to
reach a decision. As a result of the full text filtering 47 papers were selected
to be included.

>>>>

Based on the research questions and intended focus of the research, we defined
four facets to guide inclusion/exclusion decisions: agile software engineering,
focus on transformation, large scale, and empiricality. The first facet covers
primary studies focusing on software engineering organizations applying or
striving to apply agile methods. The second facet states that included studies
must provide insights relevant to organizational transformation, and
specifically to the research questions. The third facet underlines the
particular contribution we aim to provide with this research, namely the
exclusive focus on large organizations. The fourth facet limits inclusion to
studies presenting real world cases. These four facets were used for inclusion
and exclusion in each study selection step, including search string design,
filtering by abstracts, and full text filtering.

Table \ref{table:facets} lists the facets and gives examples on matching topics
and not relevant topics. For a study to be included it needed to be relevant
in all facets. Even if a study discussed some of the irrelevant topics it could
be included as long as it had some content matcing all the facets.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.20\textwidth}
                     >{\raggedright\arraybackslash}p{0.34\textwidth}
                     >{\raggedright\arraybackslash}p{0.33\textwidth} }
        \toprule
        Facet  &  Relevant topics  &  Not relevant topics  \\
        \midrule
        Agile software development  & 
                The organization develops software;
                The development method introduced is agile  &

                Agile manufacturing;
                Scrum in management boards  \\

        Organizational transformation  &
                Presenting insights in the process of transformation  &

                Comparison of before and after;
                How agile is being used in large scale   \\

        Large scale    &
                At least 50 development personel or 6 teams uses agile &

                Scaling up from small;
                A single agile team in a large setting \\

        Empiricality   &
                Case studies, experience reports  &

                Textbooks, student experiments, theory papers  \\
        \bottomrule
    \end{tabular}
    \caption{Facets of inclusion criteria with examples of relevant and
             not relevant topics}
    \label{table:facets}
\end{table}

@@

Transformation and ``scaling up'' are very closely related and in some cases
they are one and the same. For instance, if transformation begins with a pilot
and spreads gradually through the organization, the process can very well be
seen as a ``scaling up'' journey. However, we excluded cases where a initially
small organization was scaled up \cite{Maranzato2012}, and discussions focusing
on processes or tools without describing organizational change \cite{Lyon2008}.
% Also [Greening 2010] on process centered viewpoint without transformation

@@

According to the facet of \emph{empiricality} we excluded studies that did not
discuss a distinguishable real world case. We excluded textbooks, studies merely
presenting theories, and other studies that did not include any case
organization. We also excluded studies of benefits or limitations of agile in
general. Lastly, we excluded student experiments as it is implausible to
simulate the dynamics of a large organization in an experiment.

@@

We constructed a search string based on the facets \emph{agile software
deveolpment} and \emph{organizational transformation}, as presented in section
\ref{sec:inclusioncriteria}. Preliminary searches had showed that picking
keywords with good precision was difficult. Therefore we decided to exclude the
facet \emph{large scale} from the keyword search, with the consequence of
increasing the manual filtering effort in the subsequent steps. Also the facet
or \emph{empiricality} could not be represented by keywords. Having a
substantial part of the matches in non-relevant areas such as agile
manufacturing, we included only articles including the term ``software'' or
articles published in relevant conferences. Instead of engineering the search
terms any further, which proved to result in excluding some relevant articles,
we chose to rely more on manual filtering. The resulting facets and keywords are
listed in Table \ref{table:searchterms}.

@@

Full text filtering was performed by evaluating each article against the four
facets of the inclusion criteria. Filtering was done in two steps. In the first
step Dikert extracted data relevant to the four facets. Based on the extracted
data 76 papers could be immediately deemed as included or excluded. The
remaining 94 papers were evaluated against the inclusion criteria by both Dikert
and Paasivaara, and a decision was made after discussing each paper separately.
In difficult cases Lassenius was consulted to reach a decision. As a result of
the full text filtering 47 papers were selected to be included.
